Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-11-13 paper/appendix.tex
appen

     Consider the B2B model from Equation $$Y = (XE + N)F$$ $N$ centred and full rank noise.

     If $F$ and $X$ are full-rank on $Img(E)$, then, the solution of B2B, $\hat H$, will minimise

     $$\min_H  \left \| X - XH\right\| ^2  + \left \| NH\right \| ^2$$ and satisfy

>>>>

     Consider the B2B model from equation \ref{eq:model} $$Y = (XE + N)F$$ with $N$ centred and full rank noise.

     If $F$ and $X$ are full-rank on $Img(E)$, then, the solution of B2B, $\hat H$ minimizes

     $$\min_H  \left \| X - XH\right\| ^2  + \left \| NH\right \| ^2$$ and satisfies
